NIRCam Flux Calibration Plan

### 2017-04-07 ms.tex
I added some notes from our discussion today on 64x64 subarray timing as well as more details on the Pan-Starrs color-magnitude diagrams.

We obtained $grizy$ Pan-Starrs photometry\citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
We also looked up the $g$ - $r$ colors

@@

>>>>

We obtained $grizy$ Pan-Starrs photometry\citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
We also looked estimated the Pan-Starrs $g$ - $r$ colors from a Pickles G2~V spectrum using \texttt{pysynphot} \citep{lim2015pysynphot}, the measured extinction shown in Table \ref{tab:clusterProp} with a Milky Way Diffuse R(V)=3.1 \citet{cardelli1989} extinction law.
Figure \ref{fig:cmdPS} shows the Pan-Starrs color magnitude diagram for the three clusters along with vertical bars with the expected solar $g$ - $r$ color for each cluster.

@@

\subsubsection{Clocking Issues for Small Subarrays}

Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017. 
There are either 2 or 3 extra (rows? pixels?) at the end of an integration due to a rounding error.
So this could change the integration time for a 64$\times$64.
This is a known bug in the ASIC micro-code.
